\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2024-03-15 TilingProjectDraft/tilingProject.tex
rewriting parts of the notes

\documentclass[prb]{revtex4-2}
\usepackage{braket,amsmath,amssymb,color,graphicx,hyperref,bookmark}
\bibliographystyle{apsrev4-2}

@@

One method of studying Hubbard models is through auxiliary models, described in the next section. Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics. For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
\begin{equation}
\label{clus_bath_siam}
\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
\end{equation}
The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).

@@

\section{Philosophy of auxiliary model methods}
The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}. In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
\begin{equation}\begin{aligned}
	\mathcal{H} = \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
\end{aligned}\end{equation}
where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively. As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
\begin{equation}\begin{aligned}
	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R}\\
		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
\end{aligned}\end{equation}
The Greens function of the full Hamiltonian can also be split in a similar fashion:
\begin{equation}\begin{aligned}
	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
\end{aligned}\end{equation}
Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).

The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
The smaller system is typically chosen such that its eigenstates are known exactly.
Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
Such a construction is shown in fig.~\ref{cluster-bath}.
\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{cluster-bath.pdf}
	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$. \textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice. The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
	\label{cluster-bath}
\end{figure}
\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}. To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site). This distinction breaks the translational symmetry of the Hubbard model. For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.

@@

	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}}\Sigma_{\vec r}(\omega) \simeq \Sigma_{\vec r = 0}(\omega)\). This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components. This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).

	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
		\[G_{i}(\omega) = \sum_k G_{k}(\omega) = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}\]
	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
\end{itemize}
The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{dmft.pdf}
\end{figure}

@@

In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model of eq.~\ref{clus_bath_siam}:
\begin{equation}
\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
\end{equation}
This model does not show any impurity phase transition - the impurity is always screened~\cite{hrk_wilson_1980,wilson1975,bullaNRGreview}. Correlation can be introduced into the auxiliary model in two ways:
\begin{itemize}
	\item[1.] The impurity or the bath can be made to have additional interaction: 
\begin{gather}
\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - \frac{1}{2}U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
\end{gather}
The additional terms are (i) a spin-exchange interaction between the impurity site and the zeroth site, and (ii) a local correlation on the zeroth site.
\item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
\begin{equation}
\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
\end{equation}

@@

\begin{figure}[!htb]
 	\centering
 	\includegraphics[width=0.6\textwidth]{gen_siam.pdf}
 	\caption{Cluster+bath construction of auxiliary model. It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink). The other sites (green) form the rest of the bath. Just the cluster and the zeroth site have onsite correlations.}
 \end{figure}
 The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice. Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
 \begin{equation}\begin{aligned}
	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
 \end{aligned}\end{equation}
where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster. To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons. The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.

@@

\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath. The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\). Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes. We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model). The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{k\sigma} \left(c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2~,
\end{aligned}\end{equation}
where \(c_{d\sigma}\) is the impurity electron operator, \(c_{k\sigma}\) is the conduction bath electron operator, \(\vec S_d\) is the impurity spin operator and \(\vec s\) is the operator for the local spin in the conduction bath. We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)). We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of a coexistence region at finite temperatures. Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\). Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero. These two ensure that the bulk model is also at half-filling. At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.

\subsection{Formal description of the tiling procedure}
We will now use the e-SIAM to recreate the Hubbard model, by tiling the lattice with instances of this auxiliary model Hamiltonian. We will now formally define the procedure. We first identify a local auxiliary model; this will act as the ``unit cell" for our tiling procedure. For this, we place the impurity orbitals at a reference site \(\vec R_0\) of our lattice, and the bath zeroth site at a nearest-neighbour site \(\vec R_0 + \vec a\), and call the corresponding e-SIAM Hamiltonian \(\mathcal{H}_\text{aux}(\vec R_0, \vec a)\). The auxiliary model at \(\vec R_0\) can then be obtained by averaging over all nearest neighbours:
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{aux}(\vec R_0) = \frac{1}{\mathcal{W}}\sum_{\vec a}\mathcal{H}_\text{aux}(\vec R_0, \vec a)~,
\end{aligned}\end{equation}
where \(\vec a\) is summed over all nearest-neighbours of \(\vec R_0\) and \(\mathcal{W}\) is the number of such nearest-neighbours. In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice. For this, we define {\it many-particle} translation operators \(T(\vec a)\) in the usual manner: for a local fermionic operator \(c(\vec r)\), we have \(T(\vec a) c(\vec r) T^\dagger(\vec a) = c(\vec r + \vec a)\). It can also work on many-particle operators: \(T(\vec a) c(\vec r^\prime) c(\vec r) T^\dagger(\vec a) = T(\vec a) c(\vec r^\prime) T^\dagger(\vec a) T(\vec a) c(\vec r) T^\dagger(\vec a) = c(\vec r^\prime + \vec a) c(\vec r + \vec a)\). It acts similarly on the auxiliary model Hamiltonian:
\begin{equation}\begin{aligned}
	T(\vec a)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec a) = \mathcal{H}_\text{aux}(\vec R_0 + \vec a)~.
\end{aligned}\end{equation}
The full bulk model can then be expressed as
\begin{equation}\begin{aligned}
	\label{tiledHamiltonian}
	\mathcal{H}_\text{full} = \sum_{\vec r}T(\vec r)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r)~ = \sum_{\vec r} \mathcal{H}_\text{aux}(\vec r) = \frac{1}{\mathcal{W}}\sum_{\vec r, \vec a}\mathcal{H}_\text{aux}(\vec r, \vec a),
\end{aligned}\end{equation}
where \(\vec r\) sums over all lattice sites.

\subsection{Tiling towards a Hubbard-Heisenberg model}

>>>>

\documentclass[reprint,hidelinks]{revtex4-2}
\usepackage{braket,amsmath,color,graphicx,bookmark,bm}
\bibliographystyle{apsrev4-2}

@@

One method of studying Hubbard models is through auxiliary models, described in the next section. Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics. For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
\begin{equation}\begin{aligned}
\label{clus_bath_siam}
\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
\end{aligned}\end{equation}
The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).

@@

\section{Philosophy of auxiliary model methods}
The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}. In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
\begin{equation}\begin{aligned}
	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} \\
		    &= \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
\end{aligned}\end{equation}
where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively. As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
\begin{widetext}
\begin{equation}\begin{aligned}
	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R} -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
\end{aligned}\end{equation}
\end{widetext}
The Greens function of the full Hamiltonian can also be split in a similar fashion:
\begin{equation}\begin{aligned}
	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
\end{aligned}\end{equation}
Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).

The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
The smaller system is typically chosen such that its eigenstates are known exactly.
Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
Such a construction is shown in fig.~\ref{cluster-bath}.
\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{cluster-bath.pdf}
	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$. \textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice. The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
	\label{cluster-bath}
\end{figure*}
\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}. To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site). This distinction breaks the translational symmetry of the Hubbard model. For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.

@@

	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{{\bf r}}e^{i \vec{k}\cdot\vec{r}}\Sigma_{{\bf r}}(\omega) \simeq \Sigma_{{\bf r} = 0}(\omega)\). This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components. This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).

	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
		\begin{equation}\begin{aligned}
		G_{i}(\omega) &= \sum_k G_{k}(\omega) \\
			      &= \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} \\
			      &= \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}
		\end{aligned}\end{equation}
	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
\end{itemize}
The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.4\textwidth]{dmft_scheme.pdf}
\end{figure}

@@

In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model of eq.~\ref{clus_bath_siam}:
\begin{equation}\begin{aligned}
\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
\end{aligned}\end{equation}
This model does not show any impurity phase transition - the impurity is always screened~\cite{hrk_wilson_1980,wilson1975,bullaNRGreview}. Correlation can be introduced into the auxiliary model in two ways:
\begin{itemize}
	\item[1.] The impurity or the bath can be made to have additional interaction: 
\begin{gather}
\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - \frac{1}{2}U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
\end{gather}
The additional terms are (i) a spin-exchange interaction between the impurity site and the zeroth site, and (ii) a local correlation on the zeroth site.
\item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
	\begin{equation}\begin{aligned}
	\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) \\
	+ \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
	\end{aligned}\end{equation}

@@

\begin{figure}[!htb]
 	\centering
 	\includegraphics[width=0.48\textwidth]{gen_siam.pdf}
 	\caption{Cluster+bath construction of auxiliary model. It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink). The other sites (green) form the rest of the bath. Just the cluster and the zeroth site have onsite correlations.}
 \end{figure}
 The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice. Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
 \begin{equation}\begin{aligned}
	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
 \end{aligned}\end{equation}
where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster. To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons. The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.

@@

\subsection{Formal description of the tiling procedure}
We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian. The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model. The local behaviour of this impurity model should reflect the essential local physics of the lattice model. Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction. We will henceforth refer to this site as the zeroth site. In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout. In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}_1\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)\). The subscript \(1\) indicates that \({\bf z}_1\) is the first zeroth site, and that there can be multiple such zeroth sites \(\left\{ {\bf z}_i \right\} \), depending on the lattice geometry. The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)~,
\end{aligned}\end{equation}
where \({\bf z}_1\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.

In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice. For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\). In terms of manybody states and operators, their action is defined as 
\begin{equation}\begin{aligned}
	T^\dagger({\bf a}) \ket{\bf r_1, \bf r_2,\ldots} &= \ket{\bf r_1 + a, \bf r_2 + a,\ldots}\\
	T^\dagger({\bf a}) \mathcal{O}\left(\bf r_1, \bf r_2,\ldots\right)T({\bf a}) &= \mathcal{O}\left(\bf r_1 + a, \bf r_2 + a,\ldots\right)~,
\end{aligned}\end{equation}
where \(\)
For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have 
\begin{equation}\begin{aligned}
	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})
\end{aligned}\end{equation}
It acts similarly on the auxiliary model Hamiltonian:
\begin{equation}\begin{aligned}
	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
\end{aligned}\end{equation}
translating all sites by the vector \({\bf a}\). The auxiliary model, being an impurity model, lacks translation symmetry. The lattice model does remain invariant under global translation operations. In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
\begin{equation}\begin{aligned}
	\label{tilingPrescription}
	\mathcal{H}_\text{full} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)T({\bf r} - {\bf r}_d)~ \\
\end{aligned}\end{equation}
where \({\bf r}\) sums over all lattice sites.

\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath. The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\). Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes. We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model). The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
\end{aligned}\end{equation}
where \(\mathcal{H}_\text{cbath} = -t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site, \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath. Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath. We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)). We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength. Note that the impurity site and the conduction bath are both at half-filling.
